---
title: "League Champion Relationships"
author: "Santiago Torres"
date: "October 21, 2016"
output: html_document
---

```{r setup, include=FALSE}
library(png)
library(igraph)
library(jsonlite)
library(dplyr)
champ_relations = fromJSON("champions.json")
path_to_files = "C:/Users/TORRES_SANT/Documents/Programming/webscrapping/champion_relationships/img_downloader/img"
```

## Exploring The Data

### Lets take a look at the data we got in our newly created .json file.

#### Number of Champions

```{r}
numChampions <- nrow(champ_relations)
numChampions
```

#### Column Names
```{r}
colnames(champ_relations)
```

I dont like the order so lets change it up.

```{r}
newchamp_relations <- champ_relations[,c(2,3,1,4)]

head(newchamp_relations)
```

```{r echo = false}
# lets try create a vector of all the champions
testVertexNames <- as.vector(newchamp_relations$champion_name)
head(testVertexNames)
# this weird format is due to the JSON data
# lets just iterate through the champion names to store the vertexNames
vertexNames <- c()

for (champ in newchamp_relations$champion_name){
  vertexNames = c(vertexNames,tolower(champ))
}
```
```{r}
# lets take a look at the names
head(vertexNames)

#However, it turns out there is a relationship with a non champion!, Kled has a friend Skarl which appears in the data
vertexNames = c(vertexNames, "skaarl")
```

In order to add our edges of friends, we have to iterate through it again
since JSON stores multiple friends in one pair with their respective champion, we cannot use the same iteration
Edges are also more complex because we have to store the champion with its edge

Here is the data for friends

## Creating the graph

### Vertex creation / Nodes

```{r}
head(newchamp_relations$friends)
# note the pair in [[2]]
# we have to create a better loop
# so we have to create an instance of the champion for each friend connection it has

#the original data 
edgeFriendsSource <- c() #empty edge for loop
edgeFriendsTarget <- c()

i = 1
f = 1

while(i <= numChampions) {
  #champName
  champName = newchamp_relations$champion_name[[i]]
  #how many friends?
  numFriends = length(newchamp_relations$friends[[i]])
  
  while (numFriends > 0 && f <= numFriends){
    if (newchamp_relations$friends[[i]][f] !="")
      {
      edgeFriendsSource = c(edgeFriendsSource,tolower(champName))
      edgeFriendsTarget = c(edgeFriendsTarget, tolower(newchamp_relations$friends[[i]][f]))
    }
    f = f + 1
    }
  f = 1
  i = i +1
}
```

```{r}
head(edgeFriendsSource)
head(edgeFriendsTarget)
```

## Create Vertex Attributes

Lets create the attributes for the faction of champions

```{r}
i = 1
f = 1
edgeFactionSource <- c() #empty edge for loop
edgeFactionTarget <- c()
while(i <= numChampions) {
  #champName
  numFactions = length(newchamp_relations$faction[i])
  for (faction in newchamp_relations$faction){
    if (f < 134) {
    if (newchamp_relations$faction[[f]] !="" && f < 134)
    {
      champName = newchamp_relations$champion_name[[f]] #133
      edgeFactionSource = c(edgeFactionSource, tolower(champName))
      edgeFactionTarget = c(edgeFactionTarget, newchamp_relations$faction[[f]])
    }
    f = f + 1
    }
  }
  i = i+1
}
head(edgeFactionSource)
head(edgeFactionTarget)
```

## Creating Connections/Edges

Lets create the rival connections for the graph

```{r}
edgeRivals <- c() #empty edge for loop

i = 1
f = 1

while(i <= numChampions) {
  #champName
  champName = newchamp_relations$champion_name[[i]]
  #how many rivals?
  numRivals = length(newchamp_relations$rivals[[i]])
  
  while (numRivals > 0 && f <= numRivals){
    if (newchamp_relations$rivals[[i]][f] !="")
      {
      edgeRivals = c(edgeRivals,tolower(champName), tolower(newchamp_relations$rivals[[i]][f]))
    }
    f = f + 1
    }
  f = 1
  i = i +1
}
edgeRivals[276] = "wukong" # it was labeled as monkeyking, which threw errors in the graph
```

## Graphing the data

```{r}
# globals
vertexSize <- 7
vLabelSize <- 1
vLabelDist <- 0
vLabelColor <- "darkblue"
vLabelFont <- 2 # bold text
vLabelDegree = -pi/2
eArrowSize <- 1
eArrowWidth<- .7
l <- layout.fruchterman.reingold
```

Graph of both

```{r}
dfEdge = as.data.frame(edgeFriendsSource, stringsAsFactors=FALSE)
dfEdge["friendsTarget"] = edgeFriendsTarget

# vertex dataframe
dfVertex = as.data.frame(vertexNames, stringsAsFactors=FALSE)
dfVertex["ID"] = vertexNames

both = graph_from_data_frame(d=dfEdge, vertices = dfVertex, directed = T)
E(both)$color <- "darkgreen" # green for friends
both <- add_edges(both, edgeRivals, attr=list(color="red")) #red for enemies

both_layout <- layout.fruchterman.reingold(both, niter=10000)

plot(both, layout = both_layout)

#awesome, it works
```

Here we add factions to the graph

```{r}
# add factions

V(both)$Faction = as.character(edgeFactionTarget[match(V(both)$name, edgeFactionSource)])
head(V(both)$Faction)
allFactions = unique(V(both)$Faction)
factionColors <- c('red',NA,'lightblue','blue','brown','gold','lawngreen','orange',NA,'purple', 'black','darkgreen','darkgray','ivory','darkblue',NA,NA,NA,NA,NA)

# add a key for colors
factionNumber <- function ( faction ) {
  match( faction, allFactions )}

V(both)$color <- factionColors[factionNumber(V(both)$Faction)]
```

graph both

```{r}
plot(both, layout = both_layout)
```

This is very ugly so let's try and fix it up.

```{r}
V(both)$size <- vertexSize
V(both)$label.cex <- vLabelSize
V(both)$label.dist <- vLabelDist
V(both)$label.color <- vLabelColor
V(both)$label.font <- vLabelFont
V(both)$label.degree = vLabelDegree
E(both)$arrow.size <- eArrowSize
E(both)$arrow.width <- eArrowWidth

plot(both, layout=both_layout, asp = 0, frame = TRUE, main = "Champion Relationships")

```

Friends graph
```{r fig.width= 18, fig.height= 18}
friends <- graph_from_data_frame(d=dfEdge, vertices = dfVertex, direct = T)

E(friends)$color <- "darkgreen" # green for friends
V(friends)$Faction = as.character(edgeFactionTarget[match(V(friends)$name, edgeFactionSource)])

#Factions added!

allFactions = unique(V(friends)$Faction)
factionColors <- c('red',NA,'lightblue','blue','brown','gold','lawngreen','orange',NA,'purple', 'black','darkgreen','darkgray','ivory','darkblue',NA,NA,NA,NA,NA)

V(friends)$color <- factionColors[factionNumber(V(friends)$Faction)]
V(friends)$size <- vertexSize
V(friends)$label.cex <- vLabelSize
V(friends)$label.dist <- vLabelDist
V(friends)$label.color <- vLabelColor
V(friends)$label.font <- vLabelFont
V(friends)$label.degree = vLabelDegree
E(friends)$arrow.size <- eArrowSize
E(friends)$arrow.width <- eArrowWidth

#pdf("friends.pdf",10,10) #saves graph as a pdf

plot(friends, frame = TRUE, main = "Champion Friendships")

# legend(x=-1.5, y=-1.1, c("Newspaper","Television", "Online News"), pch=21,
# 
#        col="#777777", pt.bg=colrs, pt.cex=2, cex=.8, bty="n", ncol=1)
```


Rivals graph
```{r fig.width= 18, fig.height= 18}

rivals <- make_empty_graph() + vertices ( vertexNames)

rivals <- add_edges(rivals, edgeRivals, attr=list(color="red")) #red for enemies
E(rivals)$color <- "darkred" # red for rivals
V(rivals)$Faction = as.character(edgeFactionTarget[match(V(rivals)$name, edgeFactionSource)])

#Factions added!

allFactions = unique(V(rivals)$Faction)
factionColors <- c('red',NA,'lightblue','blue','brown','gold','lawngreen','orange',NA,'purple', 'black','darkgreen','darkgray','ivory','darkblue',NA,NA,NA,NA,NA)

V(rivals)$color <- factionColors[factionNumber(V(rivals)$Faction)]
V(rivals)$size <- vertexSize
V(rivals)$label.cex <- vLabelSize
V(rivals)$label.dist <- vLabelDist
V(rivals)$label.color <- vLabelColor
V(rivals)$label.font <- vLabelFont
V(rivals)$label.degree = vLabelDegree
E(rivals)$arrow.size <- eArrowSize
E(rivals)$arrow.width <- eArrowWidth

plot(rivals, layout=l, asp = 0, frame = TRUE, main = "Champion Rivals")
```

## Graph Calculations

### Centrality
```{r}
centr_degree(rivals)$centralization
centr_clo(rivals, mode = "all")$centralization
head(centr_betw(rivals)$res)
centr_eigen(rivals)$centralization
```

#### Betweenness

```{r}
highest <- max(betweenness(rivals))
index_of_highest <- match(highest, betweenness(rivals))
print(index_of_highest)
rivals[[index_of_highest]]
#darius is the point of highest connection between all rivals

highest <- max(betweenness(friends))
index_of_highest <- match(highest, betweenness(friends))
print(index_of_highest) 
friends[[index_of_highest]] 
#garen between friends

highest <- max(betweenness(both)) 
index_of_highest <- match(highest, betweenness(both)) 
print(index_of_highest) 
both[[index_of_highest]] 
#garen again
```

#### Closeness Least Friends, Rivals, Both

```{r}
closest <- min(closeness(rivals))
index_of_closest <- match(closest, closeness(rivals))
print(index_of_closest)
rivals[[index_of_closest]]
#aurelionsol rivals

closest <- min(closeness(friends))
index_of_closest <- match(closest, closeness(friends))
print(index_of_closest) 
friends[[index_of_closest]] 
#aatrox friends

closest <- min(closeness(both)) 
index_of_closest <- match(closest, closeness(both)) 
print(index_of_closest) 
both[[index_of_closest]] 
#aurelionsol again
```

#### Closeness Most Friends, Rivals, Both

```{r}
most <- max(closeness(rivals))
index_of_most <- match(most, closeness(rivals))
print(index_of_most)
rivals[[index_of_most]]
#kled most rivals

most <- max(closeness(friends))
index_of_most <- match(most, closeness(friends))
print(index_of_most) 
friends[[index_of_most]] 
#ivern friends (3)

most <- max(closeness(both)) 
index_of_most <- match(most, closeness(both)) 
print(index_of_most) 
both[[index_of_most]] 
#kled again
```


#### Eigenvector Centrality, most influential vertex

```{r}
influential <- max(evcent(rivals)$vector)
index_of_influential <- match(influential, evcent(rivals)$vector)
print(index_of_influential)
rivals[[index_of_influential]]
#kled most rivals

influential <- max(evcent(friends)$vector)
index_of_influential <- match(influential, evcent(friends)$vector)
print(index_of_influential)
friends[[index_of_influential]]
#ivern friends (3)

most <- max(evcent(both)$vector)
index_of_influential <- match(influential, evcent(both)$vector)
print(index_of_influential)
both[[index_of_influential]]
#kled again
```



#### Images in Graph
```{r}
imgname <- list()
imgfilename <- list()
  
for (x in 1:134)
    {
    imgname = c(imgname, paste(vertexNames[x], ".png", sep =""))
    imgfilename <- c(imgfilename, file.path(path_to_files,imgname[[x]]))
    }
```

```{r fig.width= 18, fig.height= 18}
set.seed(1)
# arrows point to x is friends with

l <- layout.norm(layout.fruchterman.reingold(friends, niter = 500, coolexp = .6))

V(friends)$label.cex <- .01
V(friends)$size <- .008
E(friends)$arrow.size <- 1.25
#E(friends)$arrow.width <- 1

plot(friends, layout = l, frame = TRUE, main = "Champion Relationships")

img <- lapply(imgfilename, png::readPNG)

for(i in 1:nrow(l)) {  
  rasterImage(img[[i]], l[i, 1]-0.02, l[i, 2]-0.02, l[i, 1]+0.02, l[i, 2]+0.02)
}
```

```{r fig.width= 18, fig.height= 18}
set.seed(1)
# arrows point to x is friends with
l <- layout.norm(layout.fruchterman.reingold(rivals, niter = 500, coolexp = .6))


V(rivals)$label.cex <- .01
V(rivals)$size <- .008
E(rivals)$arrow.size <- 1.25
E(rivals)$arrow.width <- .5

plot(rivals, layout = l, frame = TRUE, main = "Champion Relationships")

img <- lapply(imgfilename, png::readPNG)

for(i in 1:nrow(l)) {  
  rasterImage(img[[i]], l[i, 1]-0.02, l[i, 2]-0.02, l[i, 1]+0.02, l[i, 2]+0.02)
}
```

```{r fig.width= 18, fig.height= 18}
set.seed(1)
# arrows point to x is friends with

l <- layout.norm(layout.fruchterman.reingold(both, niter = 500, coolexp = .6))


V(both)$label.cex <- .01
V(both)$size <- .008
E(both)$arrow.size <- 1.25
E(both)$arrow.width <- 1

plot(both, layout = l, frame = TRUE, main = "Champion Relationships")

img <- lapply(imgfilename, png::readPNG)

for(i in 1:nrow(l)) {  
  rasterImage(img[[i]], l[i, 1]-0.02, l[i, 2]-0.02, l[i, 1]+0.02, l[i, 2]+0.02)
}
```
