---
title: "League Champion Relationships"
author: "Santiago Torres"
date: "October 21, 2016"
output: html_document
---

```{r setup, include=FALSE}
library(png)
library(igraph)
library(jsonlite)
library(dplyr)
champ_relations = fromJSON("champions.json")
path_to_files = "C:/Users/TORRES_SANT/Documents/Programming/webscrapping/champion_relationships/R_analysis"
```

## Exploring The Data

Lets take a look at the data we got in our newly created .json file.


```{r}
#how long is this? how many champions
numChampions <- nrow(champ_relations)
numChampions

#what are the column names?
colnames(champ_relations)

# i dont like the order so lets change it up

newchamp_relations <- champ_relations[,c(2,3,1,4)]

head(newchamp_relations)

# lets try create a vector of all the champions

testVertexNames <- as.vector(newchamp_relations$champion_name)
head(testVertexNames)

#this weird format is due to the JSON data

#lets just iterate through the champion names to store the vertexNames
vertexNames <- c()

for (champ in newchamp_relations$champion_name){
  vertexNames = c(vertexNames,tolower(champ))
}

length(vertexNames) #should be 133
length(vertexNames) == numChampions
head(vertexNames)

#However, it turns out there is a relationship with a non champion!, Kled has a friend Skarl which appears in the data
vertexNames = c(vertexNames, "skaarl")

```

in order to add our edges of friends, we have to iterate through it again
since JSON stores multiple friends in one pair with their respective champion, we cannot use the same iteration
Edges are also more complex because we have to store the champion with its edge

Here is the data for friends

```{r}
head(newchamp_relations$friends)
# note the pair in [[2]]
# we have to create a better loop
# so we have to create an instance of the champion for each friend connection it has
#get champion

#the original data 
edgeFriendsSource <- c() #empty edge for loop
edgeFriendsTarget <- c()

i = 1
f = 1

while(i <= numChampions) {
  #champName
  champName = newchamp_relations$champion_name[[i]]
  #how many friends?
  numFriends = length(newchamp_relations$friends[[i]])
  
  while (numFriends > 0 && f <= numFriends){
    if (newchamp_relations$friends[[i]][f] !="")
      {
      edgeFriendsSource = c(edgeFriendsSource,tolower(champName))
      edgeFriendsTarget = c(edgeFriendsTarget, tolower(newchamp_relations$friends[[i]][f]))
    }
    f = f + 1
    }
  f = 1
  i = i +1
}
```

Lets add the attributes for the faction of champions

```{r}
i = 1
b = 1

edgeFactionList <- c() #empty edge for loop
edgeFactionListCol2 <- c()

while(i <= numChampions) {
  #champName
  numFactions = length(newchamp_relations$faction[i])
  for (faction in newchamp_relations$faction){
    if (b < 134) {
    if (newchamp_relations$faction[[b]] !="" && b < 134)
    {
      champName = newchamp_relations$champion_name[[b]] #133
      edgeFactionList = c(edgeFactionList, tolower(champName))
      edgeFactionListCol2 = c(edgeFactionListCol2, newchamp_relations$faction[[b]])
    }
    b = b + 1
    }
  }
  i = i+1
}

```

Lets add rival connections to the dataframe

```{r}
dfEdge = as.data.frame(edgeFriendsSource, stringsAsFactors=FALSE)
dfEdge["friendsTarget"] = edgeFriendsTarget
```
```{r}
# edgeRivalsSource <- c() #empty edge for loop
# edgeRivalsTarget <- c()
# 
# i = 1
# f = 1
# 
# while(i <= numChampions) {
#   #champName
#   champName = newchamp_relations$champion_name[[i]]
#   #how many rivals?
#   numRivals = length(newchamp_relations$rivals[[i]])
#   
#   while (numRivals > 0 && f <= numRivals){
#     if (newchamp_relations$rivals[[i]][f] !="")
#       {
#       edgeRivalsSource = c(edgeRivalsSource,tolower(champName))
#       edgeRivalsTarget = c(edgeRivalsTarget, tolower(newchamp_relations$rivals[[i]][f]))
#     }
#     f = f + 1
#     }
#   f = 1
#   i = i +1
# }
# dfEdge2 = as.data.frame(edgeRivalsSource, stringsAsFactors=FALSE)
# dfEdge2["rivalsTarget"] = edgeRivalsTarget
edgeRivals <- c() #empty edge for loop

i = 1
f = 1

while(i <= numChampions) {
  #champName
  champName = newchamp_relations$champion_name[[i]]
  #how many rivals?
  numRivals = length(newchamp_relations$rivals[[i]])
  
  while (numRivals > 0 && f <= numRivals){
    if (newchamp_relations$rivals[[i]][f] !="")
      {
      edgeRivals = c(edgeRivals,tolower(champName), tolower(newchamp_relations$rivals[[i]][f]))
    }
    f = f + 1
    }
  f = 1
  i = i +1
}
edgeRivals
edgeRivals[276] = "wukong" # it was labeled as monkeyking, which threw errors in the graph
# Give the attribute friend

#set rivals and friends


# vertex dataframe
dfVertex = as.data.frame(vertexNames, stringsAsFactors=FALSE)
dfVertex["ID"] = vertexNames
g = graph_from_data_frame(d=dfEdge, vertices = dfVertex, directed = T)

E(g)$color <- "green" # green for friends


g <- add_edges(g, edgeRivals, attr=list(color="red")) #red for enemies
#get.edgelist(g, names = TRUE)
L <- layout.fruchterman.reingold(g, niter=10000)
plot(g)
#awesome, it works
```

```{r}
V(g)$Faction = as.character(edgeFactionListCol2[match(V(g)$name, edgeFactionList)])
V(g)$Faction
#Factions added!
allFactions = unique(V(g)$Faction)
allFactions
factionColors <- c('red',NA,'lightblue','blue','brown','gold','lawngreen','orange',NA,'purple', 'black','darkgreen','darkgray','ivory','darkblue',NA,NA,NA,NA,NA)

# add a key for colors
factionNumber <- function ( faction ) {
  match( faction, allFactions )
}
V(g)$color <- factionColors[factionNumber(V(g)$Faction)]
```

```{r}
plot(g, layout = L)
```

This is very ugly so let's try and fix it up.

```{r}
V(g)$size <- 10
V(g)$label.cex <- .3
V(g)$label.dist <- 0
V(g)$label.color <- 'gray'
V(g)$label.font <- 2 # bold text
E(g)$arrow.size <- 0.25
E(g)$arrow.width <- .25

l = layout.fruchterman.reingold
plot(g, layout=l, asp = 0, frame = TRUE, main = "Champion Relationships")
x = 1

img <- list()
imgname <- list()
for (x in 1:2){
imgname = c(imgname, paste(vertexNames[x], ".png", sep =""))
imgfilename <- file.path(path_to_files,imgname[[x]])
aa = 1
while (aa < 2) {
    img[[aa]] <- readPNG(imgfilename[aa])
    aa = aa + 1
}
}

imgtest <- readPNG(imgfilename)

# V(g)$raster <- 
#   for (i in vcount(g)) {
#     replicate(
#   vcount(g),
#   fimgtest, 
#   simplify=FALSE)
# 
# plot(g, vertex.shape="raster")
```


```{r}
#testing images


L[,1]=(L[,1]-min(L[,1]))/(max(L[,1])-min(L[,1]))*2-1
L[,2]=(L[,2]-min(L[,2]))/(max(L[,2])-min(L[,2]))*2-1

g$raster <-replicate(vcount(g),img[[1]],simplify = FALSE)
plot(g, layout=l, asp = 0, frame = TRUE, main = "Champion Relationships", vertex.shape="raster",vertex.label=NA,
     vertex.size=25,vertex.size2=25)

#apply(L,1,function(x)rasterImage(imgtest,x[1]-0.1,x[2]-0.1,x[1]+0.1,x[2]+0.1))


g <- graph.ring(10)
# This is a complex attribute, so supply a list here
V(g)$raster <- replicate(vcount(g), imgtest, simplify=FALSE)
E(g)$color <- "green"
E(g)$width <- 5
plot(g, vertex.shape="raster", vertex.label=NA,vertex.size=1:10*5, vertex.size2=1:10*5)
```

```{r}
x=1
img <- list()
imgname <- list()
for (x in 1:length(vertexNames)){
  imgname = c(imgname, paste(vertexNames[x], ".png", sep =""))
  imgfilename <- c(imgfilename, file.path(path_to_files, imgname[[x]]))
}
x=1
while (x < length(vertexNames)) {
    img <- c(img, readPNG(imgfilename[x]))
    x = x + 1
}

V(g)$raster = img[1]
V(g)$size <- 10
V(g)$label.cex <- .3
V(g)$label.dist <- 0
V(g)$label.color <- 'gray'
V(g)$label.font <- 2 # bold text
E(g)$arrow.size <- 0.25
E(g)$arrow.width <- .25
g = graph_from_data_frame(d=dfEdge, vertices = dfVertex, directed = T)
E(g)$color <- "green" # green for friends
g <- add_edges(g, edgeRivals, attr=list(color="red")) #red for enemies
l <- layout.fruchterman.reingold(g, niter=10000)

plot(g, layout=l, asp = 0, frame = TRUE, main = "Champion Relationships")
# V(g)$raster <- replicate(vcount(g), imgtest, simplify=FALSE)
# for(i in 1:nrow(L)) {  
#   rasterImage(img[[i]], l[i, 1]-0.2, l[i, 2]-0.2, l[i, 1]+0.2, l[i, 2]+0.2)
# }
```