---
title: "League Champion Relationships"
author: "Santiago Torres"
date: "October 21, 2016"
output: html_document
---

```{r setup, include=FALSE}
library(png)
library(igraph)
library(jsonlite)
library(dplyr)
champ_relations <- fromJSON("champions_new.json")
path_to_files <- "C:/Users/Santi/OneDrive/Documents/GitHub/champion_relationships/R_analysis/img"
```
## Exploring The Data
### Lets take a look at the data we got in our newly created .json file.
#### Number of Champions

```{r}
numChampions <- nrow(champ_relations)
numChampions
```

#### Column Names
```{r}
colnames(champ_relations)
```
Read in vectors

```{r}
# lets try create a vector of all the champions
testVertexNames <- as.vector(champ_relations$champion_name)
head(testVertexNames)
# this weird format is due to the JSON data
# lets just iterate through the champion names to store the vertexNames
vertexNames <- c()

for (champ in champ_relations$champion_name){
  vertexNames <- c(vertexNames,tolower(champ))}
```
```{r}
# lets take a look at the names
head(vertexNames)
```

In order to add our edges of friends, we have to iterate through it again
since JSON stores multiple friends in one pair with their respective champion, we cannot use the same iteration
Edges are also more complex because we have to store the champion with its edge

Here is the data for friends

## Creating the graph

### Vertex creation / Nodes

```{r}
head(champ_relations$related)
# note the pair in [[2]]
# we have to create a better loop
# so we have to create an instance of the champion for each friend connection it has

#the original data 
edgeFriendsSource <- c() #empty edge for loop
edgeFriendsTarget <- c()

i <- 1
f <- 1

while(i <= numChampions) {
  #champName
  champName <- champ_relations$champion_name[[i]]
  #how many friends?
  numFriends <- length(champ_relations$related[[i]])
  while (numFriends > 0 && f <= numFriends){
    if (champ_relations$related[[i]][f] !="")
      {
      edgeFriendsSource <- c(edgeFriendsSource,tolower(champName))
      edgeFriendsTarget <- c(edgeFriendsTarget,tolower(champ_relations$related[[i]][f]))
    }
    f <- f + 1
    }
  f <- 1
  i <- i +1
}
```

```{r}
head(edgeFriendsSource)
head(edgeFriendsTarget)
```

## Create Vertex Attributes

Lets create the attributes for the faction of champions

```{r}
i <- 1
f <- 1
edgeFactionSource <- c() #empty edge for loop
edgeFactionTarget <- c()
while(i <= numChampions) {
  #champName
  numFactions <- length(champ_relations$region[i])
  for (faction in champ_relations$region){
    if (f < 151) {
    if (champ_relations$region[[f]] !="" && f < 151)
    {
      champName <- champ_relations$champion_name[[f]] #133
      edgeFactionSource <- c(edgeFactionSource, tolower(champName))
      edgeFactionTarget <- c(edgeFactionTarget, champ_relations$region[[f]])
    }
    f <- f + 1
    }
  }
  i <- i+1
}
head(edgeFactionSource)
head(edgeFactionTarget)
```

## Creating Connections/Edges
## Graphing the data

```{r}
# globals
vertexSize <- 7
vLabelSize <- 1
vLabelDist <- 0
vLabelColor <- "darkblue"
vLabelFont <- 2 # bold text
vLabelDegree = -pi/2
eArrowSize <- 1
eArrowWidth<- .7
l <- layout.fruchterman.reingold
```

Graph of both

```{r}
dfEdge <- as.data.frame(edgeFriendsSource, stringsAsFactors=FALSE)
dfEdge["friendsTarget"] <- edgeFriendsTarget

# vertex dataframe
dfVertex <- as.data.frame(vertexNames, stringsAsFactors=FALSE)
dfVertex["ID"] <- vertexNames

both <- graph_from_data_frame(d=dfEdge, vertices = dfVertex, directed = T)
E(both)$color <- "darkgreen" # green for friends
#both <- add_edges(both, edgefriends, attr=list(color="red")) #red for enemies

both_layout <- layout.fruchterman.reingold(both, niter=10000)

plot(both, layout = both_layout)

#awesome, it works
```

Here we add factions to the graph

```{r}
# add factions

V(both)$Faction = as.character(edgeFactionTarget[match(V(both)$name, edgeFactionSource)])
head(V(both)$Faction)
allFactions = unique(V(both)$Faction)
factionColors <- c('red',NA,'lightblue','blue','brown','gold','lawngreen','orange',NA,'purple', 'black','darkgreen','darkgray','ivory','darkblue',NA,NA,NA,NA,NA)

# add a key for colors
factionNumber <- function ( faction ) {
  match( faction, allFactions )}

V(both)$color <- factionColors[factionNumber(V(both)$Faction)]
```

graph both

```{r}
plot(both, layout = both_layout)
```

This is very ugly so let's try and fix it up.

```{r}
V(both)$size <- vertexSize
V(both)$label.cex <- vLabelSize
V(both)$label.dist <- vLabelDist
V(both)$label.color <- vLabelColor
V(both)$label.font <- vLabelFont
V(both)$label.degree = vLabelDegree
E(both)$arrow.size <- eArrowSize
E(both)$arrow.width <- eArrowWidth

plot(both, layout=both_layout, asp = 0, frame = TRUE, main = "Champion Relationships")

```

Friends graph
```{r fig.width= 18, fig.height= 18}
friends <- graph_from_data_frame(d=dfEdge, vertices = dfVertex, direct = T)

E(friends)$color <- "darkgreen" # green for friends
V(friends)$Faction = as.character(edgeFactionTarget[match(V(friends)$name, edgeFactionSource)])

#Factions added!

allFactions = unique(V(friends)$Faction)
factionColors <- c('red',NA,'lightblue','blue','brown','gold','lawngreen','orange',NA,'purple', 'black','darkgreen','darkgray','ivory','darkblue',NA,NA,NA,NA,NA)

V(friends)$color <- factionColors[factionNumber(V(friends)$Faction)]
V(friends)$size <- vertexSize
V(friends)$label.cex <- vLabelSize
V(friends)$label.dist <- vLabelDist
V(friends)$label.color <- vLabelColor
V(friends)$label.font <- vLabelFont
V(friends)$label.degree = vLabelDegree
E(friends)$arrow.size <- eArrowSize
E(friends)$arrow.width <- eArrowWidth

#pdf("friends.pdf",10,10) #saves graph as a pdf

plot(friends, frame = TRUE, main = "Champion Friendships")

# legend(x=-1.5, y=-1.1, c("Newspaper","Television", "Online News"), pch=21,
# 
#        col="#777777", pt.bg=colrs, pt.cex=2, cex=.8, bty="n", ncol=1)
```
## Graph Calculations

### Centrality
```{r}
centr_degree(friends)$centralization
centr_clo(friends, mode = "all")$centralization
head(centr_betw(friends)$res)
centr_eigen(friends)$centralization
```

#### Betweenness

```{r}
highest <- max(betweenness(friends))
index_of_highest <- match(highest, betweenness(friends))
print(index_of_highest)
friends[[index_of_highest]]
#darius is the point of highest connection between all friends

highest <- max(betweenness(friends))
index_of_highest <- match(highest, betweenness(friends))
print(index_of_highest) 
friends[[index_of_highest]] 
#garen between friends

highest <- max(betweenness(both)) 
index_of_highest <- match(highest, betweenness(both)) 
print(index_of_highest) 
both[[index_of_highest]] 
#garen again
```

#### Closeness Least Friends, friends, Both

```{r}
closest <- min(closeness(friends))
index_of_closest <- match(closest, closeness(friends))
print(index_of_closest)
friends[[index_of_closest]]
#aurelionsol friends

closest <- min(closeness(friends))
index_of_closest <- match(closest, closeness(friends))
print(index_of_closest) 
friends[[index_of_closest]] 
#aatrox friends

closest <- min(closeness(both)) 
index_of_closest <- match(closest, closeness(both)) 
print(index_of_closest) 
both[[index_of_closest]] 
#aurelionsol again
```

#### Closeness Most Friends, friends, Both

```{r}
most <- max(closeness(friends))
index_of_most <- match(most, closeness(friends))
print(index_of_most)
friends[[index_of_most]]
#kled most friends

most <- max(closeness(friends))
index_of_most <- match(most, closeness(friends))
print(index_of_most) 
friends[[index_of_most]] 
#ivern friends (3)

most <- max(closeness(both)) 
index_of_most <- match(most, closeness(both)) 
print(index_of_most) 
both[[index_of_most]] 
#kled again
```


#### Eigenvector Centrality, most influential vertex

```{r}
influential <- max(evcent(friends)$vector)
index_of_influential <- match(influential, evcent(friends)$vector)
print(index_of_influential)
#friends[[index_of_influential]]
#kled most friends

influential <- max(evcent(friends)$vector)
index_of_influential <- match(influential, evcent(friends)$vector)
print(index_of_influential)
friends[[index_of_influential]]
#ivern friends (3)

most <- max(evcent(both)$vector)
index_of_influential <- match(influential, evcent(both)$vector)
print(index_of_influential)
#both[[index_of_influential]]
#kled again
```



#### Images in Graph
```{r}
imgname <- list()
imgfilename <- list()
  
for (x in 1:151)
    {
    imgname = c(imgname, paste(vertexNames[x], ".png", sep =""))
    imgfilename <- c(imgfilename, file.path(path_to_files,imgname[[x]]))
    }
```

```{r fig.width= 18, fig.height= 18}
set.seed(1)
# arrows point to x is friends with

l <- layout.norm(layout.fruchterman.reingold(friends, niter = 500, coolexp = .6))

V(friends)$label.cex <- .01
V(friends)$size <- .008
E(friends)$arrow.size <- 1.25
#E(friends)$arrow.width <- 1

plot(friends, layout = l, frame = TRUE, main = "Champion Relationships")

img <- lapply(imgfilename, png::readPNG)

for(i in 1:nrow(l)) {  
  rasterImage(img[[i]], l[i, 1]-0.02, l[i, 2]-0.02, l[i, 1]+0.02, l[i, 2]+0.02)
}
```

```{r fig.width= 18, fig.height= 18}
set.seed(1)
# arrows point to x is friends with
l <- layout.norm(layout.fruchterman.reingold(friends, niter = 500, coolexp = .6))


V(friends)$label.cex <- .01
V(friends)$size <- .008
E(friends)$arrow.size <- 1.25
E(friends)$arrow.width <- .5

plot(friends, layout = l, frame = TRUE, main = "Champion Relationships")

img <- lapply(imgfilename, png::readPNG)

for(i in 1:nrow(l)) {  
  rasterImage(img[[i]], l[i, 1]-0.02, l[i, 2]-0.02, l[i, 1]+0.02, l[i, 2]+0.02)
}
```

```{r fig.width= 18, fig.height= 18}
set.seed(1)
# arrows point to x is friends with

l <- layout.norm(layout.fruchterman.reingold(both, niter = 500, coolexp = .6))


V(both)$label.cex <- .01
V(both)$size <- .008
E(both)$arrow.size <- 1.25
E(both)$arrow.width <- 1

plot(both, layout = l, frame = TRUE, main = "Champion Relationships")

img <- lapply(imgfilename, png::readPNG)

for(i in 1:nrow(l)) {  
  rasterImage(img[[i]], l[i, 1]-0.02, l[i, 2]-0.02, l[i, 1]+0.02, l[i, 2]+0.02)
}
```
