---
title: "League Champion Relationships"
author: "Santiago Torres"
date: "October 21, 2016"
output: html_document
---

```{r setup, include=FALSE}
#attempting to make this as abstract as possible for reuse.
library(png)
library(igraph)
library(jsonlite)
champ_relations = fromJSON("champions.json")
path_to_files = "C:/Users/TORRES_SANT/Documents/Programming/webscrapping/champion_relationships/R_analysis"
```

## Exploring The Data

Lets take a look at the data we got in our newly created .json file.


```{r}
#how long is this? how many champions
numChampions <- nrow(champ_relations)
numChampions

#what are the column names?
colnames(champ_relations)

# i dont like the order so lets change it up

newchamp_relations <- champ_relations[,c(2,3,1,4)]

head(newchamp_relations)

# lets try create a vector of all the champions

testVertexNames <- as.vector(newchamp_relations$champion_name)
head(testVertexNames)

#this weird format is due to the JSON data

#lets just iterate through the champion names to store the vertexNames
vertexNames <- c()

for (champ in newchamp_relations$champion_name){
  vertexNames = c(vertexNames,tolower(champ))
}

length(vertexNames) #should be 133
length(vertexNames) == numChampions
head(vertexNames)

#However, it turns out there is a relationship with a non champion!, Kled has a friend Skarl which appears in the data
vertexNames = c(vertexNames, "skaarl")

```


in order to add our edges of friends, we have to iterate through it again
since JSON stores multiple friends in one pair with their respective champion, we cannot use the same iteration
Edges are also more complex because we have to store the champion with its edge

```{r}
head(newchamp_relations$friends)
# note the pair in [[2]]
# we have to create a better loop
# so we have to create an instance of the champion for each friend connection it has
#get champion

#the original data 
edgeList <- c() #empty edge for loop
edgeListCol2 <- c()

i = 1
f = 1

while(i <= numChampions) {
  #champName
  champName = newchamp_relations$champion_name[[i]]
  #how many friends?
  numFriends = length(newchamp_relations$friends[[i]])
  
  while (numFriends > 0 && f <= numFriends){
    if (newchamp_relations$friends[[i]][f] !="")
      {
      edgeList = c(edgeList,tolower(champName))
      edgeListCol2 = c(edgeListCol2, tolower(newchamp_relations$friends[[i]][f]))
    }
    f = f + 1
    }
  f = 1
  i = i +1
  }
dfEdge = as.data.frame(edgeList, stringsAsFactors=FALSE)
dfEdge["target"] = edgeListCol2

dfVertex = as.data.frame(vertexNames, stringsAsFactors=FALSE)
dfVertex["ID"] = vertexNames
head(edgeList)

#awesome, it works
```

# Seeing the graph
## Default apparance
The easiest way to do so is to just run the `plot` function on the graph.  This will not look very good, because we haven't customized anything about the graph's appearance yet.  But let's see how it looks.

```{r}
g = graph_from_data_frame(d=dfEdge, vertices = dfVertex, directed = T)
plot(g)
```

This is very ugly so let's try and fix it up.

```{r}
V(g)$size <- 5
V(g)$label.cex <- 0.5
plot(g)
```


```{r}
#testing images
aa = 1
img <- list()
for (x in vertexNames){
  imgname = c(imgname, paste(x, ".png", sep =""))
  imgfilename <- file.path(path_to_files, imgname)
}
while (aa <= length(vertexNames)) {
    img[[aa]] <- readPNG(imgfilename[aa])
}
layout(matrix(1:length(vertexNames),nr=4,byr=T))
for (j in 1:length(vertexNames)) plot(img[[j]])

img2filename <- file.path("C:/Users/TORRES_SANT/Documents/Programming/webscrapping/champion_relationships/R_analysis","wukong.png")

imgtest <- readPNG(img2filename)

g <- graph.ring(10)
# This is a complex attribute, so supply a list here
V(g)$raster <- replicate(vcount(g), imgtest, simplify=FALSE)
plot(g, vertex.shape="raster", vertex.label=NA,vertex.size=1:10*5, vertex.size2=1:10*5)
```
    